Make manuscript figures

### 2021-10-28 scripts/R/make_manuscript_figures.rmd
add subtitle labels to spvl tree figure

png(file = paste(FIGDIR, "spvl_on_tree.png", sep = "/"),
    height = height, width = linewidth,
    units = "cm",
    res = 300)
plot_grid(v_tree + theme(legend.position = "none"),
          h_tree + theme(legend.position = "none"),
          spvl_tree_same_scale + theme(legend.position = "none"),
          get_legend(v_tree), get_legend(h_tree), get_legend(spvl_tree_same_scale),
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(3, 1))
dev.off()
```

>>>>

png(file = paste(FIGDIR, "spvl_on_tree.png", sep = "/"),
    height = height, width = linewidth,
    units = "cm",
    res = 300)
plot_grid(spvl_tree_same_scale + theme(legend.position = "none"),
          h_tree + theme(legend.position = "none"),
          v_tree + theme(legend.position = "none"),
          get_legend(spvl_tree_same_scale), get_legend(h_tree), get_legend(v_tree),
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(3, 1),
          labels = c("A", "B", "C", "", "", ""))
dev.off()
```
